Online {\IterComp}

### 2017-09-08 related.tex
updates motivation

Chen~\etal~\cite{chen10,chen12a} evaluate the effectiveness of iterative compilations across a large number of input test cases.
Their main motivation is to answer the question:
\textit{How data input dependent is {\itercomp}?}
Their results show that it is possible to find a combination of compiler optimisations that achieves at least 86\% of the maximum speedup across all input test cases.
These optimal combinations are program-specific and yield average speedups up to 3.75$\times$ over the highest optimisation level of compilers.

When optimising a program, the main method for {\itercomp} used by Chen~\etal~\cite{chen10,chen12a} evaluates each combination of compiler optimisations across all the available inputs, i.e., if $N$ is the number of input test cases and $M$ is the total number of combinations of compiler optimisations, they perform a total of $O(NM)$ runs of the program being optimised.
Furthermore, they use a pre-defined set of only 300 different combinations of compiler optimisations, which represents a very small sample of the optimisation search space for most modern compilers, e.g.
LLVM has 56 distinct optimisation passes and GCC has about 47 high-level (SSA form) optimisation passes and about 25 low-level (RTL) optimisation passes, which in both cases result in much more than $2^{50}$ distinct combinations of compiler optimisations, without considering repetition.

Recent work~\cite{chen12b,fang15} have applied the same idea of performing input-dependent {\itercomp} to distributed applications on data centres.
In summary, each worker receives a subset of the input dataset, called the evaluation dataset, to perform an \textit{online} {\itercomp} of the code being executed.
Each worker performs the same the method for {\itercomp} used by Chen~\etal~\cite{chen10,chen12a}, i.e., they evaluate each combination of compiler optimisations across all the evaluation dataset.
However, because the optimisation is performed online, they usually consider a small evaluation dataset and a small number of compiler optimisations.

Fursin~\etal~\cite{fursin07} addressed the problem of comparing the effect of two optimisations on two distinct inputs. For that purpose, they proposed to use instruction per cycle (IPC) as the metric for performing such comparison.
Their result show that using IPC seems promising as a robust metric for {\itercomp} across large input datasets.
However, some specific optimisation techniques may affect the use of IPC as a robust metric, and specially IPC has been shown to provide poor performance estimation for multi-threaded programs~\cite{alameldeen06,eyerman08}.
In particular, IPC can give a skewed performance measure if threads spend time in \textit{spin-lock loops} or other synchronisation mechanisms.
Some existing work on performance assessment suggest that total execution time should be used for measuring performance of multi-threaded programs~\cite{alameldeen06,eyerman08}.
Aalameldeen and Wood~\cite{alameldeen06} in particular suggest that a simple work-related metric should be used if the unit of work is representative enough.
Work-related metrics have already been largely used for measuring performance of throughput-oriented applications, for other applications, however, choosing an appropriate unit of work can be more challenging~\cite{alameldeen06}.

@@

Goldsmith~\etal~\cite{goldsmith07} use \textit{block frequency} as the measure for performance for empirically describing the asymptotic behaviour of programs, which is known as empirical computational complexity.
Block frequency is a relative metric that represents the number of times a basic block executes~\cite{ball94,ball96}.
They argue in favour of block frequency due to its portability, repeatability and exactness, since it does not suffer from timer resolution problems or non-deterministic noises.
Block frequency also has the advantage of being efficiently profiled by means of automatic code instrumentation~\cite{knuth73,ball94}.

However, in the context of comparing different optimisations, although block frequency would be able to capture aspects of optimisations that simplify the control-flow graph (CFG), measuring work at the basic block resolution would not capture effects of optimisations at the instruction level.
Because of that, we extend the idea of using basic block frequency to measure computational work by also considering the computational cost of each basic block.
The computational cost of a basic block is given by weighing the instructions that it contains.

>>>>

Chen~\etal~\cite{chen10,chen12a} evaluate the effectiveness of iterative compilations across a large number of input test cases.
Their main motivation is to answer the question:
\textit{How data input dependent is {\itercomp}?}
Their results show that it is possible to find a combination of compiler optimizations that achieves at least 86\% of the maximum speedup across all input test cases.
These optimal combinations are program-specific and yield average speedups up to 3.75$\times$ over the highest optimization level of compilers.

When optimising a program, the main method for {\itercomp} used by Chen~\etal~\cite{chen10,chen12a} evaluates each combination of compiler optimizations across all the available inputs, i.e., if $N$ is the number of input test cases and $M$ is the total number of combinations of compiler optimizations, they perform a total of $O(NM)$ runs of the program being optimized.
Furthermore, they use a pre-defined set of only 300 different combinations of compiler optimizations, which represents a very small sample of the optimization search space for most modern compilers, e.g.
LLVM has 56 distinct optimization passes and GCC has about 47 high-level (SSA form) optimization passes and about 25 low-level (RTL) optimization passes, which in both cases result in much more than $2^{50}$ distinct combinations of compiler optimizations, without considering repetition.

Recent work~\cite{chen12b,fang15} have applied the same idea of performing input-dependent {\itercomp} to distributed applications on data centres.
In summary, each worker receives a subset of the input dataset, called the evaluation dataset, to perform an \textit{online} {\itercomp} of the code being executed.
Each worker performs the same the method for {\itercomp} used by Chen~\etal~\cite{chen10,chen12a}, i.e., they evaluate each combination of compiler optimizations across all the evaluation dataset.
However, because the optimization is performed online, they usually consider a small evaluation dataset and a small number of compiler optimizations.

Fursin~\etal~\cite{fursin07} addressed the problem of comparing the effect of two optimizations on two distinct inputs. For that purpose, they proposed to use instruction per cycle (IPC) as the metric for performing such comparison.
Their result show that using IPC seems promising as a robust metric for {\itercomp} across large input datasets.
However, some specific optimization techniques may affect the use of IPC as a robust metric, and specially IPC has been shown to provide poor performance estimation for multi-threaded programs~\cite{alameldeen06,eyerman08}.
In particular, IPC can give a skewed performance measure if threads spend time in \textit{spin-lock loops} or other synchronisation mechanisms.
Some existing work on performance assessment suggest that total execution time should be used for measuring performance of multi-threaded programs~\cite{alameldeen06,eyerman08}.
Aalameldeen and Wood~\cite{alameldeen06} in particular suggest that a simple work-related metric should be used if the unit of work is representative enough.
Work-related metrics have already been largely used for measuring performance of throughput-oriented applications, for other applications, however, choosing an appropriate unit of work can be more challenging~\cite{alameldeen06}.

@@

Goldsmith~\etal~\cite{goldsmith07} use \textit{block frequency} as the measure for performance for empirically describing the asymptotic behavior of programs, which is known as empirical computational complexity.
Block frequency is a relative metric that represents the number of times a basic block executes~\cite{ball94,ball96}.
They argue in favor of block frequency due to its portability, repeatability and exactness, since it does not suffer from timer resolution problems or non-deterministic noises.
Block frequency also has the advantage of being efficiently profiled by means of automatic code instrumentation~\cite{knuth73,ball94}.

However, in the context of comparing different optimizations, although block frequency would be able to capture aspects of optimizations that simplify the control-flow graph (CFG), measuring work at the basic block resolution would not capture effects of optimizations at the instruction level.
Because of that, we extend the idea of using basic block frequency to measure computational work by also considering the computational cost of each basic block.
The computational cost of a basic block is given by weighing the instructions that it contains.

### 2017-09-08 results.tex
updates motivation

For the evaluation of the performance overhead that the instrumentation incur to the benchmarks, we measure the wall-clock time of the benchmarks when compiled with the default {\flagstype -O3} optimisation.
For each benchmark, we compute the average overhead over all its 1000 input dataset.
When measuring the wall-clock time for each input, in order to reduce noise, we execute the same input until we have a statistically sound measurement, i.e. we execute until we have an interval no larger than 1\% with 99\% confidence.
Figure~\ref{fig:overhead-O3} shows the performance overhead imposed by the work instrumentation on the benchmarks when compared to their non-instrumented counterparts.
Figure~\ref{fig:overhead-improvement-O3} indicates the improvement of the relaxation algorithm over the optimal instrumentation, regarding the reduction in overhead.

@@

For comparison, we use four configurations\footnote{A configuration using the WPO relaxation was not used due to the time necessary for executing the experiments.}.
In all configurations, the same optimisation sequence is used for multiple inputs, using a dynamic input-window size, as explained in Section~\ref{sec:oic-infra}.
The average performance over the input window provides an estimate for the overall performance of the optimisation sequence across distinct inputs.
The optimisation sequences are ranked based on their average performance, and the best optimisation sequence is selected.
%When selecting the best optimisation sequence, they are ranked by the average of their performance measurement, using the WP metric, except for the Oracle-RM which uses the real speedup over \texttt{-O0}.
\begin{itemize}
\item \textbf{Oracle-RM} executes the program multiple times for each input, measuring the real speedup for each optimisation sequence, and then uses the real speedup over {\flagstype -O0} for comparing the optimisation sequences.
  The speedups are computed based on the wall-clock time.
  In order to reduce noise, the program is executed several times for the same input, until the confidence interval was no larger than 1\% for a 99\% confidence.
\item \textbf{Oracle-PP} represents an oracle with a \textit{perfect} non-intrusive profiling.
  Although it uses the WP metric for comparing optimisation sequences, this oracle also avoids noise in its measurements by also executing the program multiple times for each input.
  The first execution is used for profiling the work metric.
  The remaining executions are used for measuring the wall-clock time without using the work profiling.
\item \textbf{Real-OP} corresponds to the online {\itercomp} as it would be applied in a real online scenario.
  For each optimisation, a random sample of inputs is selected, and the program is executed only once with each input.
  When executing each input, it uses the optimal work instrumentation for profiling the work metric.
  The average of the WP for the sample of inputs is then used for selecting the best optimisation.
\item \textbf{Real-R5} is similar to the {Real-OP}.
  It also corresponds to the online {\itercomp} as it would be applied in a real online scenario.
  For each optimisation, a random sample of inputs is selected, and the program is executed only once with each input.
  When executing each input, it uses the relaxed work instrumentation, with a 5\% threshold, for profiling the work metric.
  The average of the WP for the sample of inputs is then used for selecting the best optimisation.
\item \textbf{Real-IPC} corresponds to the online {\itercomp} based on the IPC metric.
  For each optimisation, a random sample of inputs is selected, and the program is executed only once with each input.
  The average of the IPC metric for the sample of inputs is then used for selecting the best optimisation.
\end{itemize}
The comparison between Oracle-RM and Oracle-PP is useful for validating the use of the WP metric for guiding {\itercomp}, while the other configurations demonstrate the viability of applying the online {\itercomp} in a real scenario.

@@

\subsection{The Set of Optimisation Sequences}

For the purpose of evaluating the use of the WP metric with {\itercomp}, we collected in advance a fixed set of optimisation sequences.
The reason for using this fixed set, as explained in Section~\ref{sec:oic-infra}, is because this paper is focused on other components of the infrastructure for performing {\itercomp} and we assume that a good generator of optimisation sequences will be used in a real online scenario.
This set contains 500 optimisation sequences collected in a random search using the training benchmarks.
These optimisation sequences contain an average of 40 individual optimisation passes, including repetitions, with a maximum of 119 optimisation passes, but it also contains optimisation sequences which consist of a single flag, such as the default optimisations {\flagstype -O1}, {\flagstype -O2}, {\flagstype -O3}, {\flagstype -Os}, and {\flagstype -Oz}.

  % \begin{minipage}{0.9\textwidth}
  %    \vspace{1em}
  %    \noindent\textbf{Example of a short optimisation sequence:}\vspace{-1ex}
  %    \justify{\flagstype -mem2reg -simplifycfg -constprop -dce}
  % \end{minipage}
  %
  % \begin{minipage}{0.9\textwidth}
  %    \vspace{1em}
  %    \noindent\textbf{Example of a long optimisation sequence:}\vspace{-1ex}
  %    \justify{\flagstype -globalopt -reassociate -instcombine -loop-rotate -block-freq -deadargelim -early-cse -sroa -argpromotion -sccp -tbaa -barrier -constmerge \mbox{-loop-vectorize} -domtree -basicaa -memdep -basiccg -memcpyopt \mbox{-constprop} -adce -globaldce -mem2reg -constmerge \mbox{-globaldce} -constprop -instsimplify -dse -dce -simplifycfg -loop-unroll -reassociate -constprop \mbox{-globaldce} -instsimplify -adce -constmerge -bb-vectorize -dce -mergefunc -simplifycfg -dse -loop-unroll -globaldce}
  % \end{minipage}
  %
  % \begin{minipage}{0.9\textwidth}
  %    \vspace{1em}
  %    \noindent\textbf{Example of an optimisation sequence which includes {-O3}:}\vspace{-1ex}
  %    \justify{\flagstype -O3 -adce -globaldce -simplifycfg -memcpyopt -reassociate -mergefunc \mbox{-dce} -dse}
  %    \vspace{2em}
  % \end{minipage}

Repeating the same optimisation pass can be beneficial and usually expected by other passes.
For example, the {\flagstype -loop-simplify} pass is used for transforming loops into a canonical form by inserting pre-header and exit basic blocks.
Although this pass inserts jumps due to redundant basic blocks, this canonical form can be favourable to other loop optimisations.
Because of the redundant basic blocks, this optimisation pass expects that the {\flagstype -simplifycfg} will eventually be executor later on the optimisation pipeline.
Another example of such inter-relation between transformations concerns the {\flagstype -licm} and {\flagstype -mem2reg} passes.
The {\flagstype -licm} pass is responsible for moving invariant code out from the loop body.
It usually creates new local variables, using memory access operations, for assisting with the code manipulation, which means that the executing the {\flagstype -mem2reg} pass afterwards would be useful as a cleanup pass for removing the extra memory accesses generated.
However, many of the analysis required for identifying loop invariant also benefit from the transformations performed by the {\flagstype -mem2reg} pass.
These examples illustrate the importance of repeating optimisation passes.
Moreover, they illustrate the intricate relation amongst several transformations.

However, all optimisation sequences in the set of optimisations were generated completely at random, without using any knowledge of individual transformations.
Each optimisation sequence was generated in two steps: \textit{(1)} randomly selects the number of flags; \textit{(2)} randomly selects the flags, allowing repetitions.
Afterwards, this randomly generated optimisation sequence would be included in the set of optimisation sequences only if it was able to improve the performance of a training benchmark, also selected at random, in respect of the {\flagstype -O3} default optimisation.
This process was repeated until we obtained all the 500 distinct optimisation sequences.

@@

In order to evaluate the quality of the final optimisation sequences selected by the {\itercomp} search, we compare their speedup by measuring wall-clock time of the benchmarks when compiled with the standard {\flagstype -O3} optimisation.
For each benchmark, after selecting the final optimisation sequence, we compute the average speedup over all the 1000 input dataset.
When measuring the wall-clock time for each input, to reduce noise, we execute the same input until we have a statistically sound measurement, i.e. we execute until we have an interval no larger than 1\% with 99\% confidence.
Figure~\ref{fig:speedups} shows these average speedups over all the 1000 input dataset.
This figure shows that the best optimisation sequence selected with the Oracle-PP is very close to the performance of the best optimisation sequence selected with the Oracle-RM.
This result is important for demonstrating that a work-based metric has the potential to produce good results in a real online scenario, where there is the restriction that programs execute distinct inputs only once.
Moreover, the evaluation also indicates that the use of relaxation algorithms does not degrade the optimisation search,
it might even benefit the {\itercomp} as it tends to insert smaller interferences in the performance measurement.
Finally, Figure~\ref{fig:speedups} also presents the results of {\itercomp} guided by IPC, which is futher discussed in Figure~\ref{fig:ipc-vs-work}.

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{figs/speedups.pdf}
    \caption{Speedups obtained from the final optimisation sequence selected by the online {\itercomp}.
	         The speedups reported for each benchmark represents the average speedup across their complete 1000 input datasets.}
    \label{fig:speedups}
\end{figure*}

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{figs/ipc-vs-work.pdf}
    \caption{Comparison between {\itercomp} using IPC or the WP metric.}
    \label{fig:ipc-vs-work}
\end{figure*}

Figure~\ref{fig:ipc-vs-work} presents a comparison between IPC and the WP metric regarding their correlation with the actual speedup over \verb|-O0| observed during {\itercomp}.
Each point in the figure corresponds to each metric averaged over input windows collected during multiple executions of the {\itercomp}.
The vertical lines correspond to the optimisation sequence selected by the {\itercomp} search, which either represents the highest IPC or the highest value of WP.
In all cases, the optimisation sequence selected based on the WP is much closer to the best speedup than the optimisation sequence selected based on IPC, which can be attributed to the fact that the WP has a stronger correlation with the speedup.
In all cases, IPC shows little to no correlation with the speedup, which corroborates the argument given in Section~\ref{sec:ipc-vs-work-metric}.

For some cases, namely for the tiff-related benchmarks, the WP shows a worse correlation with speedup.
We believe these cases could be improved by improving the cost model used to compute the work metric.
However, even in these cases, the optimisation sequences selected based on the WP outperform those selected based on the IPC metric.

>>>>

For the evaluation of the performance overhead that the instrumentation incur to the benchmarks, we measure the wall-clock time of the benchmarks when compiled with the default {\flagstype -O3} optimization.
For each benchmark, we compute the average overhead over all its 1000 input dataset.
When measuring the wall-clock time for each input, in order to reduce noise, we execute the same input until we have a statistically sound measurement, i.e. we execute until we have an interval no larger than 1\% with 99\% confidence.
Figure~\ref{fig:overhead-O3} shows the performance overhead imposed by the work instrumentation on the benchmarks when compared to their non-instrumented counterparts.
Figure~\ref{fig:overhead-improvement-O3} indicates the improvement of the relaxation algorithm over the optimal instrumentation, regarding the reduction in overhead.

@@

For comparison, we use four configurations\footnote{A configuration using the WPO relaxation was not used due to the time necessary for executing the experiments.}.
In all configurations, the same optimization sequence is used for multiple inputs, using a dynamic input-window size, as explained in Section~\ref{sec:oic-infra}.
The average performance over the input window provides an estimate for the overall performance of the optimization sequence across distinct inputs.
The optimization sequences are ranked based on their average performance, and the best optimization sequence is selected.
%When selecting the best optimization sequence, they are ranked by the average of their performance measurement, using the WP metric, except for the Oracle-RM which uses the real speedup over \texttt{-O0}.
\begin{itemize}
\item \textbf{Oracle-RM} executes the program multiple times for each input, measuring the real speedup for each optimization sequence, and then uses the real speedup over {\flagstype -O0} for comparing the optimization sequences.
  The speedups are computed based on the wall-clock time.
  In order to reduce noise, the program is executed several times for the same input, until the confidence interval was no larger than 1\% for a 99\% confidence.
\item \textbf{Oracle-PP} represents an oracle with a \textit{perfect} non-intrusive profiling.
  Although it uses the WP metric for comparing optimization sequences, this oracle also avoids noise in its measurements by also executing the program multiple times for each input.
  The first execution is used for profiling the work metric.
  The remaining executions are used for measuring the wall-clock time without using the work profiling.
\item \textbf{Real-OP} corresponds to the online {\itercomp} as it would be applied in a real online scenario.
  For each optimization, a random sample of inputs is selected, and the program is executed only once with each input.
  When executing each input, it uses the optimal work instrumentation for profiling the work metric.
  The average of the WP for the sample of inputs is then used for selecting the best optimization.
\item \textbf{Real-R5} is similar to the {Real-OP}.
  It also corresponds to the online {\itercomp} as it would be applied in a real online scenario.
  For each optimization, a random sample of inputs is selected, and the program is executed only once with each input.
  When executing each input, it uses the relaxed work instrumentation, with a 5\% threshold, for profiling the work metric.
  The average of the WP for the sample of inputs is then used for selecting the best optimization.
\item \textbf{Real-IPC} corresponds to the online {\itercomp} based on the IPC metric.
  For each optimization, a random sample of inputs is selected, and the program is executed only once with each input.
  The average of the IPC metric for the sample of inputs is then used for selecting the best optimization.
\end{itemize}
The comparison between Oracle-RM and Oracle-PP is useful for validating the use of the WP metric for guiding {\itercomp}, while the other configurations demonstrate the viability of applying the online {\itercomp} in a real scenario.

@@

\subsection{The Set of Optimization Sequences}

For the purpose of evaluating the use of the WP metric with {\itercomp}, we collected in advance a fixed set of optimization sequences.
The reason for using this fixed set, as explained in Section~\ref{sec:oic-infra}, is because this paper is focused on other components of the infrastructure for performing {\itercomp} and we assume that a good generator of optimization sequences will be used in a real online scenario.
This set contains 500 optimization sequences collected in a random search using the training benchmarks.
These optimization sequences contain an average of 40 individual optimization passes, including repetitions, with a maximum of 119 optimization passes, but it also contains optimization sequences which consist of a single flag, such as the default optimizations {\flagstype -O1}, {\flagstype -O2}, {\flagstype -O3}, {\flagstype -Os}, and {\flagstype -Oz}.

  % \begin{minipage}{0.9\textwidth}
  %    \vspace{1em}
  %    \noindent\textbf{Example of a short optimization sequence:}\vspace{-1ex}
  %    \justify{\flagstype -mem2reg -simplifycfg -constprop -dce}
  % \end{minipage}
  %
  % \begin{minipage}{0.9\textwidth}
  %    \vspace{1em}
  %    \noindent\textbf{Example of a long optimization sequence:}\vspace{-1ex}
  %    \justify{\flagstype -globalopt -reassociate -instcombine -loop-rotate -block-freq -deadargelim -early-cse -sroa -argpromotion -sccp -tbaa -barrier -constmerge \mbox{-loop-vectorize} -domtree -basicaa -memdep -basiccg -memcpyopt \mbox{-constprop} -adce -globaldce -mem2reg -constmerge \mbox{-globaldce} -constprop -instsimplify -dse -dce -simplifycfg -loop-unroll -reassociate -constprop \mbox{-globaldce} -instsimplify -adce -constmerge -bb-vectorize -dce -mergefunc -simplifycfg -dse -loop-unroll -globaldce}
  % \end{minipage}
  %
  % \begin{minipage}{0.9\textwidth}
  %    \vspace{1em}
  %    \noindent\textbf{Example of an optimization sequence which includes {-O3}:}\vspace{-1ex}
  %    \justify{\flagstype -O3 -adce -globaldce -simplifycfg -memcpyopt -reassociate -mergefunc \mbox{-dce} -dse}
  %    \vspace{2em}
  % \end{minipage}

Repeating the same optimization pass can be beneficial and usually expected by other passes.
For example, the {\flagstype -loop-simplify} pass is used for transforming loops into a canonical form by inserting pre-header and exit basic blocks.
Although this pass inserts jumps due to redundant basic blocks, this canonical form can be favourable to other loop optimizations.
Because of the redundant basic blocks, this optimization pass expects that the {\flagstype -simplifycfg} will eventually be executor later on the optimization pipeline.
Another example of such inter-relation between transformations concerns the {\flagstype -licm} and {\flagstype -mem2reg} passes.
The {\flagstype -licm} pass is responsible for moving invariant code out from the loop body.
It usually creates new local variables, using memory access operations, for assisting with the code manipulation, which means that the executing the {\flagstype -mem2reg} pass afterwards would be useful as a cleanup pass for removing the extra memory accesses generated.
However, many of the analysis required for identifying loop invariant also benefit from the transformations performed by the {\flagstype -mem2reg} pass.
These examples illustrate the importance of repeating optimization passes.
Moreover, they illustrate the intricate relation amongst several transformations.

However, all optimization sequences in the set of optimizations were generated completely at random, without using any knowledge of individual transformations.
Each optimization sequence was generated in two steps: \textit{(1)} randomly selects the number of flags; \textit{(2)} randomly selects the flags, allowing repetitions.
Afterwards, this randomly generated optimization sequence would be included in the set of optimization sequences only if it was able to improve the performance of a training benchmark, also selected at random, in respect of the {\flagstype -O3} default optimization.
This process was repeated until we obtained all the 500 distinct optimization sequences.

@@

In order to evaluate the quality of the final optimization sequences selected by the {\itercomp} search, we compare their speedup by measuring wall-clock time of the benchmarks when compiled with the standard {\flagstype -O3} optimization.
For each benchmark, after selecting the final optimization sequence, we compute the average speedup over all the 1000 input dataset.
When measuring the wall-clock time for each input, to reduce noise, we execute the same input until we have a statistically sound measurement, i.e. we execute until we have an interval no larger than 1\% with 99\% confidence.
Figure~\ref{fig:speedups} shows these average speedups over all the 1000 input dataset.
This figure shows that the best optimization sequence selected with the Oracle-PP is very close to the performance of the best optimization sequence selected with the Oracle-RM.
This result is important for demonstrating that a work-based metric has the potential to produce good results in a real online scenario, where there is the restriction that programs execute distinct inputs only once.
Moreover, the evaluation also indicates that the use of relaxation algorithms does not degrade the optimization search,
it might even benefit the {\itercomp} as it tends to insert smaller interferences in the performance measurement.
Finally, Figure~\ref{fig:speedups} also presents the results of {\itercomp} guided by IPC, which is futher discussed in Figure~\ref{fig:ipc-vs-work}.

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{figs/speedups.pdf}
    \caption{Speedups obtained from the final optimization sequence selected by the online {\itercomp}.
	         The speedups reported for each benchmark represents the average speedup across their complete 1000 input datasets.}
    \label{fig:speedups}
\end{figure*}

%\begin{figure*}[h]
%    \centering
%    \includegraphics[width=\textwidth]{figs/ipc-vs-work.pdf}
%    \caption{Comparison between {\itercomp} using IPC or the WP metric.}
%    \label{fig:ipc-vs-work}
%\end{figure*}

%Figure~\ref{fig:ipc-vs-work} presents a comparison between IPC and the WP metric regarding their correlation with the actual speedup over \verb|-O0| observed during {\itercomp}.
%Each point in the figure corresponds to each metric averaged over input windows collected during multiple executions of the {\itercomp}.
%The vertical lines correspond to the optimization sequence selected by the {\itercomp} search, which either represents the highest IPC or the highest value of WP.
%In all cases, the optimization sequence selected based on the WP is much closer to the best speedup than the optimization sequence selected based on IPC, which can be attributed to the fact that the WP has a stronger correlation with the speedup.
%In all cases, IPC shows little to no correlation with the speedup, which corroborates the argument given in Section~\ref{sec:ipc-vs-work-metric}.

%For some cases, namely for the tiff-related benchmarks, the WP shows a worse correlation with speedup.
%We believe these cases could be improved by improving the cost model used to compute the work metric.
%However, even in these cases, the optimization sequences selected based on the WP outperform those selected based on the IPC metric.
